
\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.7in,top=0.4in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {./images/} }

\hypersetup{
    urlbordercolor=1 1 1
}

%----------------------------------------------------------------------------------------
%   DOCUMENT START
%----------------------------------------------------------------------------------------
\name{Carlos Menezes} % Your name
\address{(+351)\ 968543707 \\ carlos-menezes212@hotmail.com \\ \url{https://www.carlos-menezes.com}} % Your phone number and email
\begin{document}
\title{Carlos Menezes - Resumé}
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{University of Madeira}{September 2018 - June 2020}{Associate's Degree in Networks and Computer Systems (score: 19)}{Funchal, Madeira}
\vspace{-.15cm}
Final score: 19 \\
\textbf{Subjects:} Network Security, Operating Systems, Distributed Systems, Wireless Networks, Wide Area Networks, Network Management, Digital Systems, Computer Architecture.
\item[]
\end{rSubsection}

\vspace{-.2cm}

\begin{rSubsection}{University of Madeira}{September 2020 - currently}{Bachelor in Computer Science}{Funchal, Madeira}
\vspace{-.15cm}
\textbf{Subjects:} Calculus I, Programming Paradigms, Discrete Maths, Mechanics and Waves, Numerical Methods and Operations Research, Data Structures and Algorithms, Object Oriented Programming, Probability and Statistics, Database Management Systems, Computational Logic, Operating Systems.
\item[]
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Altice Labs}{March 2020 - June 2020}{Software Engineer Intern}{Remote}
Delivering key telecommunications technologies since 1950, Altice Labs has been shaping the future of technology, enabling Communications Service Providers and Enterprises to offer advanced and differentiated services to their customers and users.
\item Use tools such as sngrep, SIPp and Jira;
\item Developed a C++ application using Asterisk's REST Interface (ARI) that provides call control, audio playback and audio recording;
\end{rSubsection}

\begin{rSubsection}{Porto Santo Municipality}{August 2021}{Summer Internship}{Porto Santo}
\item Automated image unskewing of large document scans (over 25 documents with over 100 pages) leveraging a Python script, OpenCV and ImageMagick.
\end{rSubsection}

\end{rSection}
%----------------------------------------------------------------------------------------
%   TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Strengths}

Although I can easily adapt to new technologies, technological stacks/infrastructure and tools, I've included the tools I use the most on my day-to-day necessities or side projects. I have a huge interest in learning new technologies as a mean of accelerating a team's workflow and product delivery.

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Rust, C++, TypeScript, JavaScript, Python, \LaTeX, SQL \\
Software & Excel, Git, WireShark, sngrep, Docker, Cisco Packet Tracer, Photoshop\\
\end{tabular}

\end{rSection}

\begin{rSection}{Recommendations}

\begin{paragraph}{}
\textbf{Luís Rodolfo Serrado Gomes Marques de Sousa, no. 0000002131, May 27\textsuperscript{th} 2021, Teacher at University of Madeira}
\\
\\
''I had the opportunity to first meet Carlos Menezes at University of Madeira, at CTeSP in the "Operating Systems Introduction" classroom. From the beginning, Carlos was one of the top students. In the Distributed Systems class, Carlos got the top place, not only as a student, but also as a good friend of his classmates, always helping after finishing his assignments.
\\
\\
As predicted, Carlos got easy access to the studies for the degree on Computer Engineering, based on the grades he had in CTeSP. As I heard, he is having success, not only on the grades and classmates friendship, but also as a reference student.
\\
\\
Given my experience as a teacher, I strongly recommend him for his future professional endeavours as I believe he is well prepared to embrace new professional challenges and become an asset.''
\end{paragraph}

\end{rSection}

\end{document}
